---
title: "Peak Calling cutoff (TOP2B and P53)"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

## **📌 TOP2B broad peaks (before deduplication)**
```{r TOP, echo=TRUE, fig.width=16, fig.height=10}
library(tidyverse)
library(readr)
library(scales)   # <- needed for label_number()

# --- metadata ---
metadata <- tribble(
  ~Sample,           ~Sample_Det,
  "MCW_SP_ChIP27",   "Ind1_VEH_TOP2B",
  "MCW_SP_ChIP28",   "Ind1_DOX_TOP2B",
  "MCW_SP_ChIP31",   "Ind2_VEH_TOP2B",
  "MCW_SP_ChIP32",   "Ind2_DOX_TOP2B",
  "MCW_SP_ChIP39",   "Ind3_VEH_TOP2B",
  "MCW_SP_ChIP40",   "Ind3_DOX_TOP2B",
  "MCW_SP_ChIP43",   "Ind4_VEH_TOP2B",
  "MCW_SP_ChIP44",   "Ind4_DOX_TOP2B",
  "MCW_SP_ChIP51",   "Ind5_VEH_TOP2B",
  "MCW_SP_ChIP52",   "Ind5_DOX_TOP2B",
  "MCW_SP_ChIP55",   "Ind6_VEH_TOP2B",
  "MCW_SP_ChIP56",   "Ind6_DOX_TOP2B"
) |> mutate(
  Sample     = factor(Sample,     levels = Sample),
  Sample_Det = factor(Sample_Det, levels = Sample_Det)
)

# --- load all cutoff analysis files ---
files <- list.files("data/macs3_broad_out_TOP2B",
                    pattern = "_cutoff_analysis\\.txt$", full.names = TRUE)

df <- files |>
  set_names() |>
  map_dfr(~ read_delim(.x, delim = "\t", show_col_types = FALSE), .id = "filepath") |>
  mutate(Sample = basename(filepath) |> str_remove("_cutoff_analysis\\.txt")) |>
  left_join(metadata, by = "Sample") |>
  mutate(Sample_Det = factor(Sample_Det, levels = levels(metadata$Sample_Det))) |>
  arrange(Sample_Det, qscore)

# Common x-scale (guarantees tick at 0)
x_fixed <- scale_x_continuous(
  limits = c(0, 7),
  breaks = 0:7,
  labels = as.character(0:7),
  expand = c(0, 0)
)

# ---- Plot with linear y-axis ----
p_linear <- ggplot(df, aes(qscore, npeaks, group = Sample)) +
  geom_line(size = 0.8, color = "#d95f02") +
  facet_wrap(~ Sample_Det, scales = "free_y", ncol = 6) +
  x_fixed +
  scale_y_continuous(labels = scales::label_number(big.mark = ",")) +
  labs(x = "Q Score", y = "Peak Counts (linear)") +
  theme_minimal(base_size = 12) +
  theme(strip.text = element_text(face = "bold", size = 10),
        panel.grid.minor = element_blank())

# ---- Plot with log10 y-axis ----
p_log <- df |>
  mutate(npeaks = ifelse(npeaks <= 0, NA, npeaks)) |>
  ggplot(aes(qscore, npeaks, group = Sample)) +
  geom_line(size = 0.8, color = "#d95f02") +
  facet_wrap(~ Sample_Det, scales = "free_y", ncol = 6) +
  x_fixed +
  scale_y_log10(labels = scales::label_number(big.mark = ",")) +
  labs(x = "Q Score", y = "Peak Counts (log10)") +
  theme_minimal(base_size = 12) +
  theme(strip.text = element_text(face = "bold", size = 10),
        panel.grid.minor = element_blank())

# ---- Print both ----
p_linear
p_log
```


## **📌 TOP2B narrow peaks (before deduplication)**
```{r TOP2, echo=TRUE, fig.width=16, fig.height=10}
library(tidyverse)
library(readr)

# --- metadata ---
metadata <- tribble(
  ~Sample,           ~Sample_Det,
  "MCW_SP_ChIP27",   "Ind1_VEH_TOP2B",
  "MCW_SP_ChIP28",   "Ind1_DOX_TOP2B",
  "MCW_SP_ChIP31",   "Ind2_VEH_TOP2B",
  "MCW_SP_ChIP32",   "Ind2_DOX_TOP2B",
  "MCW_SP_ChIP39",   "Ind3_VEH_TOP2B",
  "MCW_SP_ChIP40",   "Ind3_DOX_TOP2B",
  "MCW_SP_ChIP43",   "Ind4_VEH_TOP2B",
  "MCW_SP_ChIP44",   "Ind4_DOX_TOP2B",
  "MCW_SP_ChIP51",   "Ind5_VEH_TOP2B",
  "MCW_SP_ChIP52",   "Ind5_DOX_TOP2B",
  "MCW_SP_ChIP55",   "Ind6_VEH_TOP2B",
  "MCW_SP_ChIP56",   "Ind6_DOX_TOP2B"
)

# --- load all cutoff analysis files ---
files <- list.files("data/macs3_narrow_out_TOP2B", pattern = "_cutoff_analysis\\.txt$", full.names = TRUE)

df <- files %>%
  set_names() %>%
  map_dfr(~ read_delim(.x, delim = "\t", show_col_types = FALSE), .id = "filepath") %>%
  mutate(Sample = basename(filepath) %>% str_remove("_cutoff_analysis\\.txt")) %>%
  left_join(metadata, by = "Sample")

# ---- Plot with linear y-axis ----
p_linear <- df %>%
  ggplot(aes(x = qscore, y = npeaks, group = Sample)) +
  geom_line(size = 0.8, color = "#d95f02") +
  facet_wrap(~ Sample_Det, scales = "free_y", ncol = 6) +
  scale_x_continuous(
    limits = c(0, 7),
    breaks = 0:7,
    labels = as.character(0:7),   # ensures "0" shows up
    expand = c(0, 0)
  ) +
  scale_y_continuous(labels = label_number(big.mark = ",")) +
  labs(x = "Q Score", y = "Peak Counts (linear)") +
  theme_minimal(base_size = 12) +
  theme(
    strip.text = element_text(face = "bold", size = 10),
    panel.grid.minor = element_blank()
  )

# ---- Plot with log10 y-axis ----
p_log <- df %>%
  ggplot(aes(x = qscore, y = npeaks, group = Sample)) +
  geom_line(size = 0.8, color = "#d95f02") +
  facet_wrap(~ Sample_Det, scales = "free_y", ncol = 6) +
  scale_x_continuous(
    limits = c(0, 7),
    breaks = 0:7,
    labels = as.character(0:7),
    expand = c(0, 0)
  ) +
  scale_y_log10(labels = label_number(big.mark = ",")) +
  labs(x = "Q Score", y = "Peak Counts (log10)") +
  theme_minimal(base_size = 12) +
  theme(
    strip.text = element_text(face = "bold", size = 10),
    panel.grid.minor = element_blank()
  )

# ---- Print both ----
p_linear
p_log
```

## **📌 P53 narrow peaks (before deduplication)**
```{r P53, echo=TRUE, fig.width=16, fig.height=10}

library(tidyverse)
library(readr)
library(scales)

# --- metadata for p53 ---
metadata_p53 <- tribble(
  ~Sample,           ~Sample_Det,
  "MCW_SP_ChIP29",   "Ind1_VEH_p53",
  "MCW_SP_ChIP30",   "Ind1_DOX_p53",
  "MCW_SP_ChIP33",   "Ind2_VEH_p53",
  "MCW_SP_ChIP34",   "Ind2_DOX_p53",
  "MCW_SP_ChIP41",   "Ind3_VEH_p53",
  "MCW_SP_ChIP42",   "Ind3_DOX_p53",
  "MCW_SP_ChIP45",   "Ind4_VEH_p53",
  "MCW_SP_ChIP46",   "Ind4_DOX_p53",
  "MCW_SP_ChIP53",   "Ind5_VEH_p53",
  "MCW_SP_ChIP54",   "Ind5_DOX_p53",
  "MCW_SP_ChIP57",   "Ind6_VEH_p53",
  "MCW_SP_ChIP58",   "Ind6_DOX_p53"
) %>%
  mutate(
    Sample     = factor(Sample,     levels = Sample),
    Sample_Det = factor(Sample_Det, levels = Sample_Det)
  )

# --- load all cutoff-analysis files (edit path if needed) ---
data_dir <- "data/macs3_narrow_out_P53"   # <— change if your folder name differs
files <- list.files(data_dir, pattern = "_cutoff_analysis\\.txt$", full.names = TRUE)

df_p53 <- files %>%
  set_names() %>%
  map_dfr(~ read_delim(.x, delim = "\t", show_col_types = FALSE), .id = "filepath") %>%
  mutate(Sample = basename(filepath) %>% str_remove("_cutoff_analysis\\.txt")) %>%
  left_join(metadata_p53, by = "Sample") %>%
  mutate(Sample_Det = factor(Sample_Det, levels = levels(metadata_p53$Sample_Det))) %>%
  arrange(Sample_Det, qscore)

# --------- common x scale (forces 0..7 with a printed 0) ----------
x_fixed <- scale_x_continuous(
  limits = c(0, 7),
  breaks = 0:7,
  labels = as.character(0:7),
  expand = c(0, 0)
)

# ---- linear y ----
p_linear_p53 <- ggplot(df_p53, aes(qscore, npeaks, group = Sample)) +
  geom_line(size = 0.8, color = "#d95f02") +
  facet_wrap(~ Sample_Det, scales = "free_y", ncol = 6) +
  x_fixed +
  scale_y_continuous(labels = label_number(big.mark = ",")) +
  labs(x = "Q Score", y = "Peak Counts (linear)") +
  theme_minimal(base_size = 12) +
  theme(
    strip.text = element_text(face = "bold", size = 10),
    panel.grid.minor = element_blank()
  )

# ---- log10 y ----
p_log_p53 <- ggplot(df_p53, aes(qscore, npeaks, group = Sample)) +
  geom_line(size = 0.8, color = "#d95f02") +
  facet_wrap(~ Sample_Det, scales = "free_y", ncol = 6) +
  x_fixed +
  scale_y_log10(labels = label_number(big.mark = ",")) +
  labs(x = "Q Score", y = "Peak Counts (log10)") +
  theme_minimal(base_size = 12) +
  theme(
    strip.text = element_text(face = "bold", size = 10),
    panel.grid.minor = element_blank()
  )

# ---- show both ----
p_linear_p53
p_log_p53
```

## **📌 TOP2B broad peaks (after deduplication)**
```{r TOP_dedup, echo=TRUE, fig.width=16, fig.height=10}
library(tidyverse)
library(readr)

# --- metadata ---
metadata <- tribble(
  ~Sample,           ~Sample_Det,
  "MCW_SP_ChIP27",   "Ind1_VEH_TOP2B",
  "MCW_SP_ChIP28",   "Ind1_DOX_TOP2B",
  "MCW_SP_ChIP31",   "Ind2_VEH_TOP2B",
  "MCW_SP_ChIP32",   "Ind2_DOX_TOP2B",
  "MCW_SP_ChIP39",   "Ind3_VEH_TOP2B",
  "MCW_SP_ChIP40",   "Ind3_DOX_TOP2B",
  "MCW_SP_ChIP43",   "Ind4_VEH_TOP2B",
  "MCW_SP_ChIP44",   "Ind4_DOX_TOP2B",
  "MCW_SP_ChIP51",   "Ind5_VEH_TOP2B",
  "MCW_SP_ChIP52",   "Ind5_DOX_TOP2B",
  "MCW_SP_ChIP55",   "Ind6_VEH_TOP2B",
  "MCW_SP_ChIP56",   "Ind6_DOX_TOP2B"
)

# --- load all cutoff analysis files ---
files <- list.files("data/macs3_broad_out_TOP2B_dedup", pattern = "_cutoff_analysis\\.txt$", full.names = TRUE)

df <- files %>%
  set_names() %>%
  map_dfr(~ read_delim(.x, delim = "\t", show_col_types = FALSE), .id = "filepath") %>%
  mutate(Sample = basename(filepath) %>% str_remove("_cutoff_analysis\\.txt")) %>%
  left_join(metadata, by = "Sample")

# ---- Plot with linear y-axis ----
p_linear <- df %>%
  ggplot(aes(x = qscore, y = npeaks, group = Sample)) +
  geom_line(size = 0.8, color = "#d95f02") +
  facet_wrap(~ Sample_Det, scales = "free_y", ncol = 6) +
  scale_x_continuous(
    limits = c(0, 7),
    breaks = 0:7,
    labels = as.character(0:7),   # ensures "0" shows up
    expand = c(0, 0)
  ) +
  scale_y_continuous(labels = label_number(big.mark = ",")) +
  labs(x = "Q Score", y = "Peak Counts (linear)") +
  theme_minimal(base_size = 12) +
  theme(
    strip.text = element_text(face = "bold", size = 10),
    panel.grid.minor = element_blank()
  )

# ---- Plot with log10 y-axis ----
p_log <- df %>%
  ggplot(aes(x = qscore, y = npeaks, group = Sample)) +
  geom_line(size = 0.8, color = "#d95f02") +
  facet_wrap(~ Sample_Det, scales = "free_y", ncol = 6) +
  scale_x_continuous(
    limits = c(0, 7),
    breaks = 0:7,
    labels = as.character(0:7),
    expand = c(0, 0)
  ) +
  scale_y_log10(labels = label_number(big.mark = ",")) +
  labs(x = "Q Score", y = "Peak Counts (log10)") +
  theme_minimal(base_size = 12) +
  theme(
    strip.text = element_text(face = "bold", size = 10),
    panel.grid.minor = element_blank()
  )

# ---- Print both ----
p_linear
p_log
```

## **📌 TOP2B narrow peaks (after deduplication)**
```{r TOP_dedup1, echo=TRUE, fig.width=16, fig.height=10}
library(tidyverse)
library(readr)

# --- metadata ---
metadata <- tribble(
  ~Sample,           ~Sample_Det,
  "MCW_SP_ChIP27",   "Ind1_VEH_TOP2B",
  "MCW_SP_ChIP28",   "Ind1_DOX_TOP2B",
  "MCW_SP_ChIP31",   "Ind2_VEH_TOP2B",
  "MCW_SP_ChIP32",   "Ind2_DOX_TOP2B",
  "MCW_SP_ChIP39",   "Ind3_VEH_TOP2B",
  "MCW_SP_ChIP40",   "Ind3_DOX_TOP2B",
  "MCW_SP_ChIP43",   "Ind4_VEH_TOP2B",
  "MCW_SP_ChIP44",   "Ind4_DOX_TOP2B",
  "MCW_SP_ChIP51",   "Ind5_VEH_TOP2B",
  "MCW_SP_ChIP52",   "Ind5_DOX_TOP2B",
  "MCW_SP_ChIP55",   "Ind6_VEH_TOP2B",
  "MCW_SP_ChIP56",   "Ind6_DOX_TOP2B"
)

# --- load all cutoff analysis files ---
files <- list.files("data/macs3_narrow_out_TOP2B_dedup", pattern = "_cutoff_analysis\\.txt$", full.names = TRUE)

df <- files %>%
  set_names() %>%
  map_dfr(~ read_delim(.x, delim = "\t", show_col_types = FALSE), .id = "filepath") %>%
  mutate(Sample = basename(filepath) %>% str_remove("_cutoff_analysis\\.txt")) %>%
  left_join(metadata, by = "Sample")

# ---- Plot with linear y-axis ----
p_linear <- df %>%
  ggplot(aes(x = qscore, y = npeaks, group = Sample)) +
  geom_line(size = 0.8, color = "#d95f02") +
  facet_wrap(~ Sample_Det, scales = "free_y", ncol = 6) +
  scale_x_continuous(
    limits = c(0, 7),
    breaks = 0:7,
    labels = as.character(0:7),   # ensures "0" shows up
    expand = c(0, 0)
  ) +
  scale_y_continuous(labels = label_number(big.mark = ",")) +
  labs(x = "Q Score", y = "Peak Counts (linear)") +
  theme_minimal(base_size = 12) +
  theme(
    strip.text = element_text(face = "bold", size = 10),
    panel.grid.minor = element_blank()
  )

# ---- Plot with log10 y-axis ----
p_log <- df %>%
  ggplot(aes(x = qscore, y = npeaks, group = Sample)) +
  geom_line(size = 0.8, color = "#d95f02") +
  facet_wrap(~ Sample_Det, scales = "free_y", ncol = 6) +
  scale_x_continuous(
    limits = c(0, 7),
    breaks = 0:7,
    labels = as.character(0:7),
    expand = c(0, 0)
  ) +
  scale_y_log10(labels = label_number(big.mark = ",")) +
  labs(x = "Q Score", y = "Peak Counts (log10)") +
  theme_minimal(base_size = 12) +
  theme(
    strip.text = element_text(face = "bold", size = 10),
    panel.grid.minor = element_blank()
  )

# ---- Print both ----
p_linear
p_log
```

## **📌 P53 narrow peaks (after deduplication)**
```{r P53_1, echo=TRUE, fig.width=16, fig.height=10}

library(tidyverse)
library(readr)
library(scales)

# --- metadata for p53 ---
metadata_p53 <- tribble(
  ~Sample,           ~Sample_Det,
  "MCW_SP_ChIP29",   "Ind1_VEH_p53",
  "MCW_SP_ChIP30",   "Ind1_DOX_p53",
  "MCW_SP_ChIP33",   "Ind2_VEH_p53",
  "MCW_SP_ChIP34",   "Ind2_DOX_p53",
  "MCW_SP_ChIP41",   "Ind3_VEH_p53",
  "MCW_SP_ChIP42",   "Ind3_DOX_p53",
  "MCW_SP_ChIP45",   "Ind4_VEH_p53",
  "MCW_SP_ChIP46",   "Ind4_DOX_p53",
  "MCW_SP_ChIP53",   "Ind5_VEH_p53",
  "MCW_SP_ChIP54",   "Ind5_DOX_p53",
  "MCW_SP_ChIP57",   "Ind6_VEH_p53",
  "MCW_SP_ChIP58",   "Ind6_DOX_p53"
) %>%
  mutate(
    Sample     = factor(Sample,     levels = Sample),
    Sample_Det = factor(Sample_Det, levels = Sample_Det)
  )

# --- load all cutoff-analysis files (edit path if needed) ---
data_dir <- "data/macs3_narrow_out_P53_dedup"   # <— change if your folder name differs
files <- list.files(data_dir, pattern = "_cutoff_analysis\\.txt$", full.names = TRUE)

df_p53 <- files %>%
  set_names() %>%
  map_dfr(~ read_delim(.x, delim = "\t", show_col_types = FALSE), .id = "filepath") %>%
  mutate(Sample = basename(filepath) %>% str_remove("_cutoff_analysis\\.txt")) %>%
  left_join(metadata_p53, by = "Sample") %>%
  mutate(Sample_Det = factor(Sample_Det, levels = levels(metadata_p53$Sample_Det))) %>%
  arrange(Sample_Det, qscore)

# --------- common x scale (forces 0..7 with a printed 0) ----------
x_fixed <- scale_x_continuous(
  limits = c(0, 7),
  breaks = 0:7,
  labels = as.character(0:7),
  expand = c(0, 0)
)

# ---- linear y ----
p_linear_p53 <- ggplot(df_p53, aes(qscore, npeaks, group = Sample)) +
  geom_line(size = 0.8, color = "#d95f02") +
  facet_wrap(~ Sample_Det, scales = "free_y", ncol = 6) +
  x_fixed +
  scale_y_continuous(labels = label_number(big.mark = ",")) +
  labs(x = "Q Score", y = "Peak Counts (linear)") +
  theme_minimal(base_size = 12) +
  theme(
    strip.text = element_text(face = "bold", size = 10),
    panel.grid.minor = element_blank()
  )

# ---- log10 y ----
p_log_p53 <- ggplot(df_p53, aes(qscore, npeaks, group = Sample)) +
  geom_line(size = 0.8, color = "#d95f02") +
  facet_wrap(~ Sample_Det, scales = "free_y", ncol = 6) +
  x_fixed +
  scale_y_log10(labels = label_number(big.mark = ",")) +
  labs(x = "Q Score", y = "Peak Counts (log10)") +
  theme_minimal(base_size = 12) +
  theme(
    strip.text = element_text(face = "bold", size = 10),
    panel.grid.minor = element_blank()
  )

# ---- show both ----
p_linear_p53
p_log_p53
```


## **📌 TOP2B broad peaks length (before deduplication)**
```{r TOP_lpeaks, echo=TRUE, fig.width=16, fig.height=10}
library(tidyverse)
library(readr)
library(scales)

# --- metadata ---
metadata <- tribble(
  ~Sample,           ~Sample_Det,
  "MCW_SP_ChIP27",   "Ind1_VEH_TOP2B",
  "MCW_SP_ChIP28",   "Ind1_DOX_TOP2B",
  "MCW_SP_ChIP31",   "Ind2_VEH_TOP2B",
  "MCW_SP_ChIP32",   "Ind2_DOX_TOP2B",
  "MCW_SP_ChIP39",   "Ind3_VEH_TOP2B",
  "MCW_SP_ChIP40",   "Ind3_DOX_TOP2B",
  "MCW_SP_ChIP43",   "Ind4_VEH_TOP2B",
  "MCW_SP_ChIP44",   "Ind4_DOX_TOP2B",
  "MCW_SP_ChIP51",   "Ind5_VEH_TOP2B",
  "MCW_SP_ChIP52",   "Ind5_DOX_TOP2B",
  "MCW_SP_ChIP55",   "Ind6_VEH_TOP2B",
  "MCW_SP_ChIP56",   "Ind6_DOX_TOP2B"
) |> mutate(
  Sample     = factor(Sample,     levels = Sample),
  Sample_Det = factor(Sample_Det, levels = Sample_Det)
)

# --- load all cutoff analysis files ---
files <- list.files("data/macs3_broad_out_TOP2B",
                    pattern = "_cutoff_analysis\\.txt$", full.names = TRUE)

df <- files |>
  set_names() |>
  map_dfr(~ read_delim(.x, delim = "\t", show_col_types = FALSE), .id = "filepath") |>
  mutate(Sample = basename(filepath) |> str_remove("_cutoff_analysis\\.txt")) |>
  left_join(metadata, by = "Sample") |>
  mutate(Sample_Det = factor(Sample_Det, levels = levels(metadata$Sample_Det))) |>
  arrange(Sample_Det, qscore)

# Common x-scale (guarantees tick at 0)
x_fixed <- scale_x_continuous(
  limits = c(0, 7),
  breaks = 0:7,
  labels = as.character(0:7),
  expand = c(0, 0)
)

# ---- Plot with linear y-axis (lpeaks) ----
p_linear <- ggplot(df, aes(qscore, lpeaks, group = Sample)) +
  geom_line(size = 0.8, color = "#d95f02") +
  facet_wrap(~ Sample_Det, scales = "free_y", ncol = 6) +
  x_fixed +
  scale_y_continuous(labels = label_number(big.mark = ",")) +
  labs(x = "Q Score", y = "Total Peak Length (bp, linear)") +
  theme_minimal(base_size = 12) +
  theme(strip.text = element_text(face = "bold", size = 10),
        panel.grid.minor = element_blank())

# ---- Plot with log10 y-axis (lpeaks) ----
p_log <- df |>
  mutate(lpeaks = ifelse(lpeaks <= 0, NA, lpeaks)) |>
  ggplot(aes(qscore, lpeaks, group = Sample)) +
  geom_line(size = 0.8, color = "#d95f02") +
  facet_wrap(~ Sample_Det, scales = "free_y", ncol = 6) +
  x_fixed +
  scale_y_log10(labels = label_number(big.mark = ",")) +
  labs(x = "Q Score", y = "Total Peak Length (bp, log10)") +
  theme_minimal(base_size = 12) +
  theme(strip.text = element_text(face = "bold", size = 10),
        panel.grid.minor = element_blank())

# ---- Print both ----
p_linear
p_log
```


## **📌 TOP2B narrow peaks length (before deduplication)**
```{r TOP2_lpeaks, echo=TRUE, fig.width=16, fig.height=10}
library(tidyverse)
library(readr)
library(scales)

# --- metadata ---
metadata <- tribble(
  ~Sample,           ~Sample_Det,
  "MCW_SP_ChIP27",   "Ind1_VEH_TOP2B",
  "MCW_SP_ChIP28",   "Ind1_DOX_TOP2B",
  "MCW_SP_ChIP31",   "Ind2_VEH_TOP2B",
  "MCW_SP_ChIP32",   "Ind2_DOX_TOP2B",
  "MCW_SP_ChIP39",   "Ind3_VEH_TOP2B",
  "MCW_SP_ChIP40",   "Ind3_DOX_TOP2B",
  "MCW_SP_ChIP43",   "Ind4_VEH_TOP2B",
  "MCW_SP_ChIP44",   "Ind4_DOX_TOP2B",
  "MCW_SP_ChIP51",   "Ind5_VEH_TOP2B",
  "MCW_SP_ChIP52",   "Ind5_DOX_TOP2B",
  "MCW_SP_ChIP55",   "Ind6_VEH_TOP2B",
  "MCW_SP_ChIP56",   "Ind6_DOX_TOP2B"
)

# --- load all cutoff analysis files ---
files <- list.files("data/macs3_narrow_out_TOP2B", pattern = "_cutoff_analysis\\.txt$", full.names = TRUE)

df <- files %>%
  set_names() %>%
  map_dfr(~ read_delim(.x, delim = "\t", show_col_types = FALSE), .id = "filepath") %>%
  mutate(Sample = basename(filepath) %>% str_remove("_cutoff_analysis\\.txt")) %>%
  left_join(metadata, by = "Sample")

# ---- Plot with linear y-axis ----
p_linear <- df %>%
  ggplot(aes(x = qscore, y = lpeaks, group = Sample)) +
  geom_line(size = 0.8, color = "#d95f02") +
  facet_wrap(~ Sample_Det, scales = "free_y", ncol = 6) +
  scale_x_continuous(
    limits = c(0, 7),
    breaks = 0:7,
    labels = as.character(0:7),
    expand = c(0, 0)
  ) +
  scale_y_continuous(labels = label_number(big.mark = ",")) +
  labs(x = "Q Score", y = "Total Peak Length (bp, linear)") +
  theme_minimal(base_size = 12) +
  theme(
    strip.text = element_text(face = "bold", size = 10),
    panel.grid.minor = element_blank()
  )

# ---- Plot with log10 y-axis ----
p_log <- df %>%
  mutate(lpeaks = ifelse(lpeaks <= 0, NA, lpeaks)) %>%
  ggplot(aes(x = qscore, y = lpeaks, group = Sample)) +
  geom_line(size = 0.8, color = "#d95f02") +
  facet_wrap(~ Sample_Det, scales = "free_y", ncol = 6) +
  scale_x_continuous(
    limits = c(0, 7),
    breaks = 0:7,
    labels = as.character(0:7),
    expand = c(0, 0)
  ) +
  scale_y_log10(labels = label_number(big.mark = ",")) +
  labs(x = "Q Score", y = "Total Peak Length (bp, log10)") +
  theme_minimal(base_size = 12) +
  theme(
    strip.text = element_text(face = "bold", size = 10),
    panel.grid.minor = element_blank()
  )

# ---- Print both ----
p_linear
p_log
```

## **📌 P53 narrow peaks length (before deduplication)**
```{r P53_length, echo=TRUE, fig.width=16, fig.height=10}

library(tidyverse)
library(readr)
library(scales)

# --- metadata for p53 ---
metadata_p53 <- tribble(
  ~Sample,           ~Sample_Det,
  "MCW_SP_ChIP29",   "Ind1_VEH_p53",
  "MCW_SP_ChIP30",   "Ind1_DOX_p53",
  "MCW_SP_ChIP33",   "Ind2_VEH_p53",
  "MCW_SP_ChIP34",   "Ind2_DOX_p53",
  "MCW_SP_ChIP41",   "Ind3_VEH_p53",
  "MCW_SP_ChIP42",   "Ind3_DOX_p53",
  "MCW_SP_ChIP45",   "Ind4_VEH_p53",
  "MCW_SP_ChIP46",   "Ind4_DOX_p53",
  "MCW_SP_ChIP53",   "Ind5_VEH_p53",
  "MCW_SP_ChIP54",   "Ind5_DOX_p53",
  "MCW_SP_ChIP57",   "Ind6_VEH_p53",
  "MCW_SP_ChIP58",   "Ind6_DOX_p53"
) %>%
  mutate(
    Sample     = factor(Sample,     levels = Sample),
    Sample_Det = factor(Sample_Det, levels = Sample_Det)
  )

# --- load all cutoff-analysis files ---
data_dir <- "data/macs3_narrow_out_P53"   # adjust if needed
files <- list.files(data_dir, pattern = "_cutoff_analysis\\.txt$", full.names = TRUE)

df_p53 <- files %>%
  set_names() %>%
  map_dfr(~ read_delim(.x, delim = "\t", show_col_types = FALSE), .id = "filepath") %>%
  mutate(Sample = basename(filepath) %>% str_remove("_cutoff_analysis\\.txt")) %>%
  left_join(metadata_p53, by = "Sample") %>%
  mutate(Sample_Det = factor(Sample_Det, levels = levels(metadata_p53$Sample_Det))) %>%
  arrange(Sample_Det, qscore)

# --------- common x scale (forces 0..7 with a printed 0) ----------
x_fixed <- scale_x_continuous(
  limits = c(0, 7),
  breaks = 0:7,
  labels = as.character(0:7),
  expand = c(0, 0)
)

# ---- linear y ----
p_linear_p53 <- ggplot(df_p53, aes(qscore, lpeaks, group = Sample)) +
  geom_line(size = 0.8, color = "#d95f02") +
  facet_wrap(~ Sample_Det, scales = "free_y", ncol = 6) +
  x_fixed +
  scale_y_continuous(labels = label_number(big.mark = ",")) +
  labs(x = "Q Score", y = "Total Peak Length (bp, linear)") +
  theme_minimal(base_size = 12) +
  theme(
    strip.text = element_text(face = "bold", size = 10),
    panel.grid.minor = element_blank()
  )

# ---- log10 y ----
p_log_p53 <- df_p53 %>%
  mutate(lpeaks = ifelse(lpeaks <= 0, NA, lpeaks)) %>%
  ggplot(aes(qscore, lpeaks, group = Sample)) +
  geom_line(size = 0.8, color = "#d95f02") +
  facet_wrap(~ Sample_Det, scales = "free_y", ncol = 6) +
  x_fixed +
  scale_y_log10(labels = label_number(big.mark = ",")) +
  labs(x = "Q Score", y = "Total Peak Length (bp, log10)") +
  theme_minimal(base_size = 12) +
  theme(
    strip.text = element_text(face = "bold", size = 10),
    panel.grid.minor = element_blank()
  )

# ---- show both ----
p_linear_p53
p_log_p53
```


## **📌 TOP2B broad peaks length (after deduplication)**
```{r TOP_dedup_length, echo=TRUE, fig.width=16, fig.height=10}
library(tidyverse)
library(readr)
library(scales)

# --- metadata ---
metadata <- tribble(
  ~Sample,           ~Sample_Det,
  "MCW_SP_ChIP27",   "Ind1_VEH_TOP2B",
  "MCW_SP_ChIP28",   "Ind1_DOX_TOP2B",
  "MCW_SP_ChIP31",   "Ind2_VEH_TOP2B",
  "MCW_SP_ChIP32",   "Ind2_DOX_TOP2B",
  "MCW_SP_ChIP39",   "Ind3_VEH_TOP2B",
  "MCW_SP_ChIP40",   "Ind3_DOX_TOP2B",
  "MCW_SP_ChIP43",   "Ind4_VEH_TOP2B",
  "MCW_SP_ChIP44",   "Ind4_DOX_TOP2B",
  "MCW_SP_ChIP51",   "Ind5_VEH_TOP2B",
  "MCW_SP_ChIP52",   "Ind5_DOX_TOP2B",
  "MCW_SP_ChIP55",   "Ind6_VEH_TOP2B",
  "MCW_SP_ChIP56",   "Ind6_DOX_TOP2B"
)

# --- load all cutoff analysis files ---
files <- list.files("data/macs3_broad_out_TOP2B_dedup", pattern = "_cutoff_analysis\\.txt$", full.names = TRUE)

df <- files %>%
  set_names() %>%
  map_dfr(~ read_delim(.x, delim = "\t", show_col_types = FALSE), .id = "filepath") %>%
  mutate(Sample = basename(filepath) %>% str_remove("_cutoff_analysis\\.txt")) %>%
  left_join(metadata, by = "Sample")

# ---- Plot with linear y-axis ----
p_linear <- df %>%
  ggplot(aes(x = qscore, y = lpeaks, group = Sample)) +
  geom_line(size = 0.8, color = "#d95f02") +
  facet_wrap(~ Sample_Det, scales = "free_y", ncol = 6) +
  scale_x_continuous(
    limits = c(0, 7),
    breaks = 0:7,
    labels = as.character(0:7),
    expand = c(0, 0)
  ) +
  scale_y_continuous(labels = label_number(big.mark = ",")) +
  labs(x = "Q Score", y = "Total Peak Length (bp, linear)") +
  theme_minimal(base_size = 12) +
  theme(
    strip.text = element_text(face = "bold", size = 10),
    panel.grid.minor = element_blank()
  )

# ---- Plot with log10 y-axis ----
p_log <- df %>%
  mutate(lpeaks = ifelse(lpeaks <= 0, NA, lpeaks)) %>%
  ggplot(aes(x = qscore, y = lpeaks, group = Sample)) +
  geom_line(size = 0.8, color = "#d95f02") +
  facet_wrap(~ Sample_Det, scales = "free_y", ncol = 6) +
  scale_x_continuous(
    limits = c(0, 7),
    breaks = 0:7,
    labels = as.character(0:7),
    expand = c(0, 0)
  ) +
  scale_y_log10(labels = label_number(big.mark = ",")) +
  labs(x = "Q Score", y = "Total Peak Length (bp, log10)") +
  theme_minimal(base_size = 12) +
  theme(
    strip.text = element_text(face = "bold", size = 10),
    panel.grid.minor = element_blank()
  )

# ---- Print both ----
p_linear
p_log
```

## **📌 TOP2B narrow peaks length (after deduplication)**
```{r TOP_dedup1_length, echo=TRUE, fig.width=16, fig.height=10}
library(tidyverse)
library(readr)
library(scales)

# --- metadata ---
metadata <- tribble(
  ~Sample,           ~Sample_Det,
  "MCW_SP_ChIP27",   "Ind1_VEH_TOP2B",
  "MCW_SP_ChIP28",   "Ind1_DOX_TOP2B",
  "MCW_SP_ChIP31",   "Ind2_VEH_TOP2B",
  "MCW_SP_ChIP32",   "Ind2_DOX_TOP2B",
  "MCW_SP_ChIP39",   "Ind3_VEH_TOP2B",
  "MCW_SP_ChIP40",   "Ind3_DOX_TOP2B",
  "MCW_SP_ChIP43",   "Ind4_VEH_TOP2B",
  "MCW_SP_ChIP44",   "Ind4_DOX_TOP2B",
  "MCW_SP_ChIP51",   "Ind5_VEH_TOP2B",
  "MCW_SP_ChIP52",   "Ind5_DOX_TOP2B",
  "MCW_SP_ChIP55",   "Ind6_VEH_TOP2B",
  "MCW_SP_ChIP56",   "Ind6_DOX_TOP2B"
)

# --- load all cutoff analysis files ---
files <- list.files("data/macs3_narrow_out_TOP2B_dedup", pattern = "_cutoff_analysis\\.txt$", full.names = TRUE)

df <- files %>%
  set_names() %>%
  map_dfr(~ read_delim(.x, delim = "\t", show_col_types = FALSE), .id = "filepath") %>%
  mutate(Sample = basename(filepath) %>% str_remove("_cutoff_analysis\\.txt")) %>%
  left_join(metadata, by = "Sample")

# ---- Plot with linear y-axis ----
p_linear <- df %>%
  ggplot(aes(x = qscore, y = lpeaks, group = Sample)) +
  geom_line(size = 0.8, color = "#d95f02") +
  facet_wrap(~ Sample_Det, scales = "free_y", ncol = 6) +
  scale_x_continuous(
    limits = c(0, 7),
    breaks = 0:7,
    labels = as.character(0:7),
    expand = c(0, 0)
  ) +
  scale_y_continuous(labels = label_number(big.mark = ",")) +
  labs(x = "Q Score", y = "Total Peak Length (bp, linear)") +
  theme_minimal(base_size = 12) +
  theme(
    strip.text = element_text(face = "bold", size = 10),
    panel.grid.minor = element_blank()
  )

# ---- Plot with log10 y-axis ----
p_log <- df %>%
  mutate(lpeaks = ifelse(lpeaks <= 0, NA, lpeaks)) %>%
  ggplot(aes(x = qscore, y = lpeaks, group = Sample)) +
  geom_line(size = 0.8, color = "#d95f02") +
  facet_wrap(~ Sample_Det, scales = "free_y", ncol = 6) +
  scale_x_continuous(
    limits = c(0, 7),
    breaks = 0:7,
    labels = as.character(0:7),
    expand = c(0, 0)
  ) +
  scale_y_log10(labels = label_number(big.mark = ",")) +
  labs(x = "Q Score", y = "Total Peak Length (bp, log10)") +
  theme_minimal(base_size = 12) +
  theme(
    strip.text = element_text(face = "bold", size = 10),
    panel.grid.minor = element_blank()
  )

# ---- Print both ----
p_linear
p_log
```

## **📌 P53 narrow peaks length (after deduplication)**
```{r P53_1_length, echo=TRUE, fig.width=16, fig.height=10}

library(tidyverse)
library(readr)
library(scales)

# --- metadata for p53 ---
metadata_p53 <- tribble(
  ~Sample,           ~Sample_Det,
  "MCW_SP_ChIP29",   "Ind1_VEH_p53",
  "MCW_SP_ChIP30",   "Ind1_DOX_p53",
  "MCW_SP_ChIP33",   "Ind2_VEH_p53",
  "MCW_SP_ChIP34",   "Ind2_DOX_p53",
  "MCW_SP_ChIP41",   "Ind3_VEH_p53",
  "MCW_SP_ChIP42",   "Ind3_DOX_p53",
  "MCW_SP_ChIP45",   "Ind4_VEH_p53",
  "MCW_SP_ChIP46",   "Ind4_DOX_p53",
  "MCW_SP_ChIP53",   "Ind5_VEH_p53",
  "MCW_SP_ChIP54",   "Ind5_DOX_p53",
  "MCW_SP_ChIP57",   "Ind6_VEH_p53",
  "MCW_SP_ChIP58",   "Ind6_DOX_p53"
) %>%
  mutate(
    Sample     = factor(Sample,     levels = Sample),
    Sample_Det = factor(Sample_Det, levels = Sample_Det)
  )

# --- load all cutoff-analysis files ---
data_dir <- "data/macs3_narrow_out_P53_dedup"
files <- list.files(data_dir, pattern = "_cutoff_analysis\\.txt$", full.names = TRUE)

df_p53 <- files %>%
  set_names() %>%
  map_dfr(~ read_delim(.x, delim = "\t", show_col_types = FALSE), .id = "filepath") %>%
  mutate(Sample = basename(filepath) %>% str_remove("_cutoff_analysis\\.txt")) %>%
  left_join(metadata_p53, by = "Sample") %>%
  mutate(Sample_Det = factor(Sample_Det, levels = levels(metadata_p53$Sample_Det))) %>%
  arrange(Sample_Det, qscore)

# --------- common x scale (forces 0..7 with a printed 0) ----------
x_fixed <- scale_x_continuous(
  limits = c(0, 7),
  breaks = 0:7,
  labels = as.character(0:7),
  expand = c(0, 0)
)

# ---- linear y (lpeaks) ----
p_linear_p53 <- ggplot(df_p53, aes(qscore, lpeaks, group = Sample)) +
  geom_line(size = 0.8, color = "#d95f02") +
  facet_wrap(~ Sample_Det, scales = "free_y", ncol = 6) +
  x_fixed +
  scale_y_continuous(labels = label_number(big.mark = ",")) +
  labs(x = "Q Score", y = "Total Peak Length (bp, linear)") +
  theme_minimal(base_size = 12) +
  theme(
    strip.text = element_text(face = "bold", size = 10),
    panel.grid.minor = element_blank()
  )

# ---- log10 y (lpeaks) ----
p_log_p53 <- df_p53 %>%
  mutate(lpeaks = ifelse(lpeaks <= 0, NA, lpeaks)) %>%
  ggplot(aes(qscore, lpeaks, group = Sample)) +
  geom_line(size = 0.8, color = "#d95f02") +
  facet_wrap(~ Sample_Det, scales = "free_y", ncol = 6) +
  x_fixed +
  scale_y_log10(labels = label_number(big.mark = ",")) +
  labs(x = "Q Score", y = "Total Peak Length (bp, log10)") +
  theme_minimal(base_size = 12) +
  theme(
    strip.text = element_text(face = "bold", size = 10),
    panel.grid.minor = element_blank()
  )

# ---- show both ----
p_linear_p53
p_log_p53
```

