---
title: "Total Reads and Mapped Reads (CTCF and RAD21)"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

## **📌 Total Reads by Sample**
### **Load Required Libraries**
```{r libraries, echo=TRUE}
# Load necessary R packages
library(edgeR)
library(limma)
library(RColorBrewer)
library(gridExtra)
library(reshape2)
library(data.table)
library(tidyverse)
library(scales)
library(biomaRt)
library(cowplot)
library(ggrepel)
library(corrplot)
library(Hmisc)
library(ggpubr)
```

## **📍 2. Load Data**
```{r load-data, echo=TRUE, message=FALSE}
align<-read.csv("data/ChIP Seq Summary stat CTCF RAD21.csv")

map<-data.frame(align)

map$Treatment<- factor(map$Treatment, levels = c("VEH_CTCF", "DOX_CTCF", "VEH_RAD21", "DOX_RAD21", "VEH_Input_P53", "DOX_Input_P53"))
```

## **📍 3. Define Color Palettes**
```{r define-colors, echo=TRUE}
drug_palc <- c("#8B006D","#DF707E","#F1B72B", "#3386DD","#707031","#41B333")

Ind_palc <- c("#ffbe0b","#ff006e","#fb5607", "#8338ec","#3a86ff","#4a4e69")

Treat_palc <- c("#ffbe0b","#ff006e","#fb5607", "#8338ec", "#800080","#FFC0CB")

Map_palc <- c("#9b19f5","#e6d800", "#b3d4ff")

Combined_palc <- c("#FF0000","#00FF00","#0000FF","#FFFF00","#FF00FF","#00FFFF","#FFA500","#800080","#FFC0CB","#A52A2A","#808080","#FFD700")

Type_palc <- c("#800080","#FFD700")
```

## **📍 4. Prepare Data**
```{r prepare-data, echo=TRUE}
# Factor Sample_name to maintain order
map$Sample.Det<-factor(map$Sample.Det,levels = map$Sample.Det)
```

## **📍 5. Plot Total Reads by Sample**
```{r plot-total-reads, echo=TRUE, message=FALSE, warning=FALSE,fig.height=8,fig.width=18}
map %>%
  #mutate(Drug=factor(Drug,levels=c("CX-5461","DOX","VEH"))) %>%
  #mutate(Conc.=factor(Conc.,levels=c("0.1","0.5"))) %>%
  #mutate(Time=factor(Time,levels=c("3","24","48"))) %>%
  #group_by(Drug,Conc.,Time) %>%
  ggplot(., aes (x =Sample.Det, y=Total.Reads..before.trimming., fill = Ind))+
  geom_col()+
  #geom_hline(aes(yintercept=20000000))+
  scale_fill_manual(values=Ind_palc)+
  scale_y_continuous(labels = label_number(suffix = " M", scale = 1e-6))+
  ggtitle(expression("Total number of reads by sample"))+
  xlab("")+
  ylab(expression("ChIP -sequencing reads"))+
  theme_bw()+
  theme(plot.title = element_text(size = rel(2), hjust = 0.5),
        axis.title = element_text(size = 15, color = "black"),
        axis.ticks = element_line(linewidth = 1.5),
        axis.line = element_line(linewidth = 1.5),
        axis.text.y = element_text(size =10, color = "black", angle = 0, hjust = 0.8, vjust = 0.5),
        axis.text.x = element_text(size =10, color = "black", angle = 90, hjust = 1, vjust = 0.2),
        #strip.text.x = element_text(size = 15, color = "black", face = "bold"),
        strip.text.y = element_text(color = "white"))
```

## **📌 Total Reads by Individuals**

```{r generate_boxplot indv, echo=TRUE, message=FALSE}
map %>%
  ggplot(aes(x = Ind, y = Total.Reads..before.trimming., fill = Ind)) +
  geom_boxplot() +
  scale_fill_manual(values = Ind_palc) +
  scale_y_continuous(labels = label_number(suffix = " M", scale = 1e-6),
                     limits = c(0, NA)) +
  ggtitle(expression("Total number of reads by Individual")) +
  xlab("") +
  ylab(expression("ChIP -sequencing reads")) +
  theme_bw() +
  theme(
    plot.title  = element_text(size = rel(2), hjust = 0.5),
    axis.title  = element_text(size = 15, color = "black"),
    axis.ticks  = element_line(linewidth = 1.5),
    axis.line   = element_line(linewidth = 1.5),
    axis.text.y = element_text(size = 10, color = "black"),
    axis.text.x = element_text(size = 10, color = "black", angle = 90,
                               hjust = 1, vjust = 0.2),
    strip.text.y = element_text(color = "white")
  )

```

## **📌 Total Reads by Treatment**
```{r generate_boxplot treatment, echo=TRUE, message=FALSE}
map %>%
  ggplot(aes(x = Treatment, y = Total.Reads..before.trimming., fill = Treatment)) +
  geom_boxplot() +
  scale_fill_manual(values = Treat_palc) +
  scale_y_continuous(labels = label_number(suffix = " M", scale = 1e-6),
                     limits = c(0, NA)) +
  ggtitle(expression("Total number of reads by Treatment")) +
  xlab("") +
  ylab(expression("ChIP -sequencing reads")) +
  theme_bw() +
  theme(
    plot.title  = element_text(size = rel(2), hjust = 0.5),
    axis.title  = element_text(size = 15, color = "black"),
    axis.ticks  = element_line(linewidth = 1.5),
    axis.line   = element_line(linewidth = 1.5),
    axis.text.y = element_text(size = 10, color = "black"),
    axis.text.x = element_text(size = 10, color = "black", angle = 90,
                               hjust = 1, vjust = 0.2),
    strip.text.y = element_text(color = "white")
  )
```

## **📌 Total Reads by Sample type**
```{r generate_boxplot type, echo=TRUE, message=FALSE}

map %>%
  ggplot(aes(x = Type, y = Total.Reads..before.trimming., fill = Type)) +
  geom_boxplot() +
  scale_fill_manual(values = Type_palc) +
  scale_y_continuous(labels = label_number(suffix = " M", scale = 1e-6),
                     limits = c(0, NA)) +
  ggtitle(expression("Total number of reads by Sample Type")) +
  xlab("") +
  ylab(expression("ChIP -sequencing reads")) +
  theme_bw() +
  theme(
    plot.title  = element_text(size = rel(2), hjust = 0.5),
    axis.title  = element_text(size = 15, color = "black"),
    axis.ticks  = element_line(linewidth = 1.5),
    axis.line   = element_line(linewidth = 1.5),
    axis.text.y = element_text(size = 10, color = "black"),
    axis.text.x = element_text(size = 10, color = "black", angle = 90,
                               hjust = 1, vjust = 0.2),
    strip.text.y = element_text(color = "white")
  )
```

## **📌 Total Reads by Individuals and Sample type**
```{r generate_boxplot Ind and type, echo=TRUE, message=FALSE}
map %>%
  ggplot(aes(x = Ind, y = Total.Reads..before.trimming., fill = Type)) +
  geom_boxplot() +
  scale_fill_manual(values = Type_palc) +
  scale_y_continuous(labels = label_number(suffix = " M", scale = 1e-6),
                     limits = c(0, NA)) +
  ggtitle(expression("Total number of reads by Individual and Sample Type")) +
  xlab("") +
  ylab(expression("ChIP -sequencing reads")) +
  theme_bw() +
  theme(
    plot.title  = element_text(size = rel(2), hjust = 0.5),
    axis.title  = element_text(size = 15, color = "black"),
    axis.ticks  = element_line(linewidth = 1.5),
    axis.line   = element_line(linewidth = 1.5),
    axis.text.y = element_text(size = 10, color = "black"),
    axis.text.x = element_text(size = 10, color = "black", angle = 90,
                               hjust = 1, vjust = 0.2),
    strip.text.y = element_text(color = "white")
  )
```

## **📌 Number of reads before and after trimming**
```{r plot trimmed reads, echo=TRUE, message=FALSE, warning=FALSE,fig.height=8,fig.width=18}
library(dplyr)
library(tidyr)
library(ggplot2)
library(scales)

# Keep sample order as in file
map$Sample.Det <- factor(map$Sample.Det, levels = map$Sample.Det)

# Make sure read counts are numeric (in case CSV parsed as character)
map <- map %>%
  mutate(
    `Total.Reads..before.trimming.` = as.numeric(`Total.Reads..before.trimming.`),
    `Total.reads..after.Trimming.`  = as.numeric(`Total.reads..after.Trimming.`)
  )

# Compute kept fraction for annotation
map <- map %>%
  mutate(kept_frac = `Total.reads..after.Trimming.` / `Total.Reads..before.trimming.`)

# Long format for before vs after
map_long <- map %>%
  pivot_longer(
    cols = c(`Total.Reads..before.trimming.`, `Total.reads..after.Trimming.`),
    names_to = "TrimStage", values_to = "Reads"
  ) %>%
  mutate(
    TrimStage = factor(
      TrimStage,
      levels = c("Total.Reads..before.trimming.", "Total.reads..after.Trimming."),
      labels = c("Before trimming", "After trimming")
    )
  )

# High-contrast (colorblind-safe) colors
stage_colors <- c("Before trimming" = "#1f78b4",  # deep blue
                  "After trimming"  = "#ff7f00")  # bright orange

# Base plot
p <- ggplot(map_long, aes(x = Sample.Det, y = Reads, fill = TrimStage)) +
  geom_col(position = position_dodge(width = 0.8), width = 0.75, color = "black") +
  scale_fill_manual(values = stage_colors) +
  scale_y_continuous(labels = label_number(suffix = " M", scale = 1e-6)) +
  ggtitle(expression("Total number of reads by sample: before vs after trimming")) +
  xlab("") +
  ylab(expression("ChIP-sequencing reads")) +
  theme_bw() +
  theme(
    plot.title  = element_text(size = rel(2), hjust = 0.5),
    axis.title  = element_text(size = 15, color = "black"),
    axis.ticks  = element_line(linewidth = 1.5),
    axis.line   = element_line(linewidth = 1.5),
    axis.text.y = element_text(size = 10, color = "black"),
    axis.text.x = element_text(size = 10, color = "black", angle = 90, hjust = 1, vjust = 0.2),
    legend.title = element_blank()
  )
p
```

## **📌 Mean Sequencing Reads Before and After Trimming by Individual, Sample Type, and Antibody**
```{r plot mean reads, echo=TRUE, message=FALSE, warning=FALSE,fig.height=12,fig.width=18}

library(dplyr)
library(tidyr)
library(ggplot2)
library(scales)
library(stringr)

# --- Prep -------------------------------------------------------------

# Use your existing data frame name: map (change to df if needed)
df <- map

# Ensure required columns exist / are numeric
df <- df %>%
  mutate(
    `Total.Reads..before.trimming.` = as.numeric(`Total.Reads..before.trimming.`),
    `Total.reads..after.Trimming.`  = as.numeric(`Total.reads..after.Trimming.`)
  )

# Define Tx if your data uses 'Treatment'
if (!"Tx" %in% names(df) && "Treatment" %in% names(df)) {
  df <- df %>% mutate(Tx = Treatment)
}

# Normalize factors you care about
df <- df %>%
  mutate(
    Ab   = ifelse(is.na(Ab) | Ab == "", "Input", as.character(Ab)),
    Type = factor(Type, levels = c("ChIP_DNA", "Input_DNA"))  # adjust if your labels differ
  )

# Helper: label function for Y axis (millions)
reads_lab <- label_number(suffix = " M", scale = 1e-6)

# Kept fraction (After / Before)
df <- df %>%
  mutate(kept_frac = `Total.reads..after.Trimming.` / `Total.Reads..before.trimming.`)

# --- Group, summarise, pivot -----------------------------------------

group_sum <- df %>%
  group_by(Ind, Type, Ab, Tx) %>%
  summarise(
    before_mean = mean(`Total.Reads..before.trimming.`, na.rm = TRUE),
    after_mean  = mean(`Total.reads..after.Trimming.`,  na.rm = TRUE),
    kept_pct    = 100 * mean(kept_frac, na.rm = TRUE),
    .groups     = "drop"
  ) %>%
  pivot_longer(
    cols      = c(before_mean, after_mean),
    names_to  = "stage",
    values_to = "reads"
  ) %>%
  mutate(
    stage = factor(stage, levels = c("before_mean", "after_mean"),
                          labels = c("Before", "After")),
    facet_id = paste0(Ind, "_", Type, "_", Ab)
  )

# Order facets by Ind then Type (cleaner viewing)
facet_levels <- group_sum %>%
  distinct(Ind, Type, Ab, facet_id) %>%
  arrange(Ind, Type, Ab) %>%
  pull(facet_id)

group_sum <- group_sum %>%
  mutate(facet_id = factor(facet_id, levels = facet_levels))

# Optional: prettier strip labels (multi-line)
strip_labeller <- function(ids) {
  parts <- str_split(ids, "_", n = 3, simplify = TRUE)
  paste0("Ind: ", parts[,1], "\nType: ", parts[,2], "\nAb: ", parts[,3])
}

# Colors for Before / After
before_after_colors <- c("Before" = "#1f78b4", "After" = "#ff7f00")

# --- Plot -------------------------------------------------------------

p_group <- ggplot(group_sum, aes(x = Tx, y = reads, fill = stage)) +
  geom_col(position = position_dodge(width = 0.8), width = 0.7, color = "black") +
  scale_fill_manual(values = before_after_colors) +
  facet_wrap(~ facet_id, scales = "free_y",
             labeller = labeller(facet_id = strip_labeller)) +
  scale_y_continuous(labels = reads_lab) +
  labs(
    x = "Treatment",
    y = "Mean reads",
    title = "Mean reads by Individual × Sample Type × Antibody"
  ) +
  theme_bw(base_size = 12) +
  theme(
    legend.title = element_blank(),
    plot.title = element_text(hjust = 0.5, face = "bold"),
    strip.text  = element_text(size = 10)
  )

p_group

```


## **📌 Duplication percentage by Sample**
```{r Dup, echo=TRUE, message=FALSE, warning=FALSE,fig.height=8,fig.width=18}
map %>%
  ggplot(aes(x = Sample.Det, y = Duplication.percentage, fill = Ind)) +
  geom_col(color = "black") +
  scale_fill_manual(values = Ind_palc) +
  scale_y_continuous(limits = c(0, 100), expand = c(0, 0)) +
  ggtitle(expression("Duplication Percentage by Sample")) +
  xlab("") +
  ylab(expression("Duplication percentage")) +
  theme_bw() +
  theme(
    plot.title  = element_text(size = rel(2), hjust = 0.5),
    axis.title  = element_text(size = 15, color = "black"),
    axis.ticks  = element_line(linewidth = 1.5),
    axis.line   = element_line(linewidth = 1.5),
    axis.text.y = element_text(size = 10, color = "black"),
    axis.text.x = element_text(size = 10, color = "black", angle = 90,
                               hjust = 1, vjust = 0.2),
    strip.text.y = element_text(color = "white")
  )
```

## **📌 Duplication percentage by Individual**
```{r Dup1, echo=TRUE, message=FALSE, warning=FALSE}

map %>%
  ggplot(aes(x = Ind, y = Duplication.percentage, fill = Ind)) +
  geom_boxplot() +
  scale_fill_manual(values = Ind_palc) +
  scale_y_continuous(limits = c(0, 100), labels = function(x) paste0(x, "%")) +
  ggtitle(expression("Duplication percentage by Individual")) +
  xlab("") +
  ylab(expression("Duplication percentage")) +
  theme_bw() +
  theme(
    plot.title  = element_text(size = rel(2), hjust = 0.5),
    axis.title  = element_text(size = 15, color = "black"),
    axis.ticks  = element_line(linewidth = 1.5),
    axis.line   = element_line(linewidth = 1.5),
    axis.text.y = element_text(size = 10, color = "black"),
    axis.text.x = element_text(size = 10, color = "black", angle = 90,
                               hjust = 1, vjust = 0.2),
    strip.text.y = element_text(color = "white")
  )
```

## **📌 Duplication percentage by Treatment**
```{r Dup2, echo=TRUE, message=FALSE, warning=FALSE}
map %>%
  ggplot(aes(x = Treatment, y = Duplication.percentage, fill = Treatment)) +
  geom_boxplot() +
  scale_fill_manual(values = Treat_palc) +
  scale_y_continuous(limits = c(0, 100), labels = function(x) paste0(x, "%")) +
  ggtitle(expression("Duplication percentage by Treatment")) +
  xlab("") +
  ylab(expression("Duplication percentage")) +
  theme_bw() +
  theme(
    plot.title  = element_text(size = rel(2), hjust = 0.5),
    axis.title  = element_text(size = 15, color = "black"),
    axis.ticks  = element_line(linewidth = 1.5),
    axis.line   = element_line(linewidth = 1.5),
    axis.text.y = element_text(size = 10, color = "black"),
    axis.text.x = element_text(size = 10, color = "black", angle = 90,
                               hjust = 1, vjust = 0.2),
    strip.text.y = element_text(color = "white")
  )

```


## **📌 Duplication percentage by Sample type**
```{r Dup3, echo=TRUE, message=FALSE, warning=FALSE}
map %>%
  ggplot(aes(x = Type, y = Duplication.percentage, fill = Type)) +
  geom_boxplot() +
  scale_fill_manual(values = Type_palc) +
  scale_y_continuous(limits = c(0, 100), labels = function(x) paste0(x, "%")) +
  ggtitle(expression("Duplication percentage by Sample Type")) +
  xlab("") +
  ylab(expression("Duplication percentage")) +
  theme_bw() +
  theme(
    plot.title  = element_text(size = rel(2), hjust = 0.5),
    axis.title  = element_text(size = 15, color = "black"),
    axis.ticks  = element_line(linewidth = 1.5),
    axis.line   = element_line(linewidth = 1.5),
    axis.text.y = element_text(size = 10, color = "black"),
    axis.text.x = element_text(size = 10, color = "black", angle = 90,
                               hjust = 1, vjust = 0.2),
    strip.text.y = element_text(color = "white")
  )

```


## **📌 Duplication percentage by Individual and Sample type**
```{r Dup4, echo=TRUE, message=FALSE, warning=FALSE}
map %>%
  ggplot(aes(x = Ind, y = Duplication.percentage, fill = Type)) +
  geom_boxplot() +
  scale_fill_manual(values = Type_palc) +
  scale_y_continuous(limits = c(0, 100), labels = function(x) paste0(x, "%")) +
  ggtitle(expression("Duplication percentage by Individual and Sample Type")) +
  xlab("") +
  ylab(expression("Duplication percentage")) +
  theme_bw() +
  theme(
    plot.title  = element_text(size = rel(2), hjust = 0.5),
    axis.title  = element_text(size = 15, color = "black"),
    axis.ticks  = element_line(linewidth = 1.5),
    axis.line   = element_line(linewidth = 1.5),
    axis.text.y = element_text(size = 10, color = "black"),
    axis.text.x = element_text(size = 10, color = "black", angle = 90,
                               hjust = 1, vjust = 0.2),
    strip.text.y = element_text(color = "white")
  )
```

## **📌 Mapping Summary**
```{r mapping, echo=TRUE, message=FALSE, warning=FALSE, ,fig.height=8,fig.width=18}

library(dplyr)
library(tidyr)
library(ggplot2)
library(scales)

# If not already done, read with check.names=TRUE so we have dot-style names
# map <- read.csv("data/ChIP Seq Summary stat TOP2B P53.csv", check.names = TRUE)

# Keep sample order as in the file
map$Sample.Det <- factor(map$Sample.Det, levels = map$Sample.Det)

# Ensure numeric (CSV can import as character)
map <- map %>%
  mutate(
    Total.Reads..before.trimming. = as.numeric(Total.Reads..before.trimming.),
    Total.reads..after.Trimming.  = as.numeric(Total.reads..after.Trimming.),
    Mapped.Reads                  = as.numeric(Mapped.Reads),
    Unmapped.reads                = as.numeric(Unmapped.reads)
  )

# Long format for the 4 metrics
metric_order <- c("Total.Reads..before.trimming.",
                  "Total.reads..after.Trimming.",
                  "Mapped.Reads",
                  "Unmapped.reads")

map_long4 <- map %>%
  dplyr::select(Sample.Det, all_of(metric_order)) %>%
  pivot_longer(cols = all_of(metric_order), names_to = "Metric", values_to = "Reads") %>%
  mutate(
    Metric = factor(
      Metric,
      levels = metric_order,
      labels = c("Before trimming", "After trimming", "Mapped reads", "Unmapped reads")
    )
  )


# Colors (colorblind-friendly)
metric_cols <- c(
  "Before trimming" = "#1f78b4",  # blue
  "After trimming"  = "#ff7f00",  # orange
  "Mapped reads"    = "#33a02c",  # green
  "Unmapped reads"  = "#6a737b"   # gray
)

# Plot: grouped bars per sample
ggplot(map_long4, aes(x = Sample.Det, y = Reads, fill = Metric)) +
  geom_col(position = position_dodge(width = 0.85), width = 0.72, color = "black") +
  scale_fill_manual(values = metric_cols) +
  scale_y_continuous(labels = label_number(suffix = " M", scale = 1e-6)) +
  labs(
    title = "Total reads per sample: Before vs After, Mapped vs Unmapped",
    x = NULL,
    y = "Reads"
  ) +
  theme_bw() +
  theme(
    plot.title  = element_text(size = rel(2), hjust = 0.5),
    axis.title  = element_text(size = 15, color = "black"),
    axis.ticks  = element_line(linewidth = 1.2),
    axis.line   = element_line(linewidth = 1.2),
    axis.text.y = element_text(size = 10, color = "black"),
    axis.text.x = element_text(size = 10, color = "black", angle = 90, hjust = 1, vjust = 0.2),
    legend.title = element_blank()
  )
```

## **📌 Total, mapped and unmapped reads by individual**
```{r mapping1, echo=TRUE, message=FALSE, warning=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(scales)

# Keep original dot-style names (assumes you read with check.names=TRUE)
# map <- read.csv("data/ChIP Seq Summary stat TOP2B P53.csv", check.names = TRUE)

# Make sure numeric
map <- map %>%
  mutate(
    Total.Reads..before.trimming. = as.numeric(Total.Reads..before.trimming.),
    Mapped.Reads                 = as.numeric(Mapped.Reads),
    Unmapped.reads               = as.numeric(Unmapped.reads)
  )

comp_cols <- c(
  "Total reads" = "#1f78b4",  # blue
  "Mapped reads"    = "#33a02c",  # green
  "Unmapped reads"  = "#6a737b"   # gray
)


# Long format for the 3 metrics
metric_order  <- c("Total.Reads..before.trimming.", "Mapped.Reads", "Unmapped.reads")
metric_labels <- c("Total reads", "Mapped reads", "Unmapped reads")

map_long3 <- map %>%
  pivot_longer(
    cols = all_of(metric_order),
    names_to = "Metric",
    values_to = "Reads"
  ) %>%
  mutate(
    Metric = factor(Metric, levels = metric_order, labels = metric_labels)
  )


ggplot(map_long3, aes(x = Ind, y = Reads, fill = Metric)) +
  geom_boxplot(position = position_dodge(width = 0.75)) +
  scale_fill_manual(values = comp_cols) +
  scale_y_continuous(labels = label_number(suffix = " M", scale = 1e-6)) +
  labs(title = "Reads by Individual: Total, mapped and Unmapped",
       x = NULL, y = "Reads") +
  theme_bw() +
  theme(plot.title = element_text(size = rel(1.8), hjust = 0.5),
        legend.title = element_blank(),
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.2))
```

## **📌 Total, mapped and unmapped reads by treatment**
```{r mapping2, echo=TRUE, message=FALSE, warning=FALSE}
ggplot(map_long3, aes(x = Treatment, y = Reads, fill = Metric)) +
  geom_boxplot(position = position_dodge(width = 0.75)) +
  scale_fill_manual(values = comp_cols) +
  scale_y_continuous(labels = label_number(suffix = " M", scale = 1e-6)) +
  labs(title = "Reads by Treatment: Total, mapped and Unmapped",
       x = NULL, y = "Reads") +
  theme_bw() +
  theme(plot.title = element_text(size = rel(1.8), hjust = 0.5),
        legend.title = element_blank(),
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.2))
```

## **📌 Total, mapped and unmapped reads by Sample type**
```{r mapping3, echo=TRUE, message=FALSE, warning=FALSE}
ggplot(map_long3, aes(x = Type, y = Reads, fill = Metric)) +
  geom_boxplot(position = position_dodge(width = 0.75)) +
  scale_fill_manual(values = comp_cols) +
  scale_y_continuous(labels = label_number(suffix = " M", scale = 1e-6)) +
  labs(title = "Reads by Sample Type: Total, mapped and Unmapped",
       x = NULL, y = "Reads") +
  theme_bw() +
  theme(plot.title = element_text(size = rel(1.8), hjust = 0.5),
        legend.title = element_blank(),
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.2))
```


## **📌 Total, mapped and unmapped reads by individual and sample type**
```{r mapping4, echo=TRUE, message=FALSE, warning=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(scales)

# Make sure numeric
map <- map %>%
  mutate(
    Total.Reads..before.trimming. = as.numeric(Total.Reads..before.trimming.),
    Mapped.Reads                  = as.numeric(Mapped.Reads),
    Unmapped.reads                = as.numeric(Unmapped.reads)
  )

# Colors for boxplot fill
comp_cols <- c(
  "Total reads" = "#1f78b4",  # blue
  "Mapped reads"    = "#33a02c",  # green
  "Unmapped reads"  = "#6a737b"   # gray
)


# Reshape into long format
map_long <- map %>%
  dplyr::select(Ind, Type,
                Total.Reads..before.trimming., Mapped.Reads, Unmapped.reads) %>%
  tidyr::pivot_longer(
    cols = c(Total.Reads..before.trimming., Mapped.Reads, Unmapped.reads),
    names_to = "Metric", values_to = "Reads"
  ) %>%
  dplyr::mutate(
    Metric = factor(Metric,
      levels = c("Total.Reads..before.trimming.", "Mapped.Reads", "Unmapped.reads"),
      labels = c("Total reads", "Mapped reads", "Unmapped reads"))
  )

# ---- Plot ----
ggplot(map_long, aes(x = Ind, y = Reads, fill = Metric)) +
  geom_boxplot(outlier.size = 0.8, position = position_dodge(width = 0.75)) +
  scale_fill_manual(values = comp_cols) +
  scale_y_continuous(labels = label_number(suffix = " M", scale = 1e-6)) +
  facet_wrap(~ Type) +
  labs(
    title = "Read mapping by Individual and Sample Type",
    x = "Individual", y = "Reads"
  ) +
  theme_bw() +
  theme(
    plot.title   = element_text(size = rel(1.6), hjust = 0.5),
    legend.title = element_blank(),
    strip.text   = element_text(size = 11, face = "bold"),
    axis.text.x  = element_text(angle = 90, hjust = 1, vjust = 0.2)
  )
```
